The imprint of global magma oceans on exoplanet demographics

### 2023-03-14 src/tex/ms.tex
Edit, provide context to occurrence rate discussion

\subsubsection{Underlying occurrence rate distributions}

Our adopted occurrence rate model \citep{Bergsten2022} changes forms at larger separations ($> \SI{50}{\watt\per\meter\squared}$) and radii ($> 1.6\,R_\oplus$) than what is relevant for the runaway greenhouse threshold, where the adopted occurrence rate density is relatively smooth.
Thus we argue that the proposed trend is not an artifact of the underlying occurrence distribution.
However, this may be different for alternative models that have sharp features in relevant regions of $R_P - S$ space. 
\todo[inline]{More discussion goes here?}

>>>>

\subsubsection{Structures in the planet occurrence rate density}
In principle, the baseline occurrence rate density in radius-period space that governs the generation of our synthetic planet sample might influence our findings, especially if it contains any features that coincide with the injected demographic feature.
This is not the case in the model from \citet{Bergsten2022} that we adopted: Its occurrence rate density is smooth in the domain relevant for the runaway greenhouse transition; discontinuities only occur at smaller instellations ($< \SI{50}{\watt\per\meter\squared}$) and larger radii ($> 1.6\,R_\oplus$).
Due to the flat occurrence rate in the region of interest, we do not expect the model underlying our planet sample to affect the recovery of the transition.
However, it should be kept in mind that any unknown sharp features in the true distribution of terrestrial planets could complicate a detection or lead to a false positive result (see Sect.~\ref{sec:dis_falsepositive}).
